<!-- R Commander Markdown Template -->

Tutorial 5
=======================

### Soh Su Xian Alicia A0114334U

### `r as.character(Sys.Date())`

```{r, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
# include this code chunk as-is to set options
knitr::opts_chunk$set(comment=NA, prompt=TRUE, out.width=750, fig.height=8, fig.width=8)
library(Rcmdr)
library(car)
library(RcmdrMisc)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
library(foreign, pos=15)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
country <- read.spss("C:/Users/Hp/Documents/country122.sav", 
  use.value.labels=TRUE, max.value.labels=Inf, to.data.frame=TRUE)
colnames(country) <- tolower(colnames(country))
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
RegModel.1 <- lm(lifeexpf~birthrat, data=country)
summary(RegModel.1)
```


Answer: Since the p-value: < 2.2e-16 (less than 0.05), this tells us that there is a linear relationship between the two variables.
From the data obtained, the correlation coefficient is 0.869 (3sf). This can be calculated by square rooting the Multiple R-squared:  0.756.
Since the value is close to 1, the linear relationship is relatively strong. 
The linear relationship is downwards (as seen from the graph below). The higher the birth rate, the lower the life expectancy.

```{r, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
scatterplot(lifeexpf~birthrat, reg.line=lm, smooth=FALSE, spread=FALSE, 
  boxplots=FALSE, span=0.5, ellipse=FALSE, levels=c(.5, .9), jitter=list(x=1),
   data=country)
```


